{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-09 Paper/main.tex
Slight language correction

	\paragraph{Monomial Basis}
	Due to the in the number of Monomial basis functions increasing collinearity, simulations were conducted up until the sixth monomial, which already shows signs of numerical instability. For reasons outlined in \ref{Monomial_basis}, they seem suited for $f_1$ where it shows a better performance than B-splines for this assumed true coefficient function. A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series. In case of $f_2$, this basis shows the weakest performance out of all basis, for which the plots in figure \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2} provide evidence. It seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries. This weakness is especially pronounced in the MSPE for $f_2,Y_1$. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) Monomial basis functions for the high(low) signal-to-noise ratio. 
	\vspace{-0.2cm}

	\paragraph{B-spline Basis}
	Simulations with B-spline basis functions were possible from 4 to 18, since from 18 onwards the simulations were running into collinearity problems.
	Function $f_1$ requires 5(4) B-spline basis functions for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis and shows the worst performance of the three basis. An explanation might be its overripe behavior at the boundaries and the exaggeration of the peculiarities of $f_1$ ( figure \ref{basis_expansion_1_1} and \ref{basis_expansion_1_2}), which is especially pronounced for the lower signal-to-noise ratio. For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratio. The B-spline basis outperforms the Monomial basis in $f_2$, but comes second to the Fourier basis. While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ ( figure \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2}). With the low signal-to-noise ratio in the responses, the simulation chooses a smaller number of basis functions, which could be to prevent fitting this scalar noise using $\hat{\beta}(t)$.
	\vspace{-0.2cm}

>>>>

	\paragraph{Monomial Basis}
	Due to the in the number of Monomial basis functions increasing collinearity, simulations were conducted up until the sixth monomial, which already shows signs of numerical instability. For reasons outlined in \ref{Monomial_basis}, they seem suited for $f_1$ where it shows a better performance than B-splines for this assumed true coefficient function. A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series. In case of $f_2$, this basis shows the weakest performance out of all basis, for which the plots in Figures \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2} provide evidence. It seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries. This weakness is especially pronounced in the MSPE for $f_2,Y_1$. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) Monomial basis functions for the high(low) signal-to-noise ratio. 
	\vspace{-0.2cm}

	\paragraph{B-spline Basis}
	Simulations with B-spline basis functions were possible from 4 to 18, since from 18 onwards the simulations were running into collinearity problems.
	Function $f_1$ requires 5(4) B-spline basis functions for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis and shows the worst performance of the three basis. An explanation might be its overripe behavior at the boundaries and the exaggeration of the peculiarities of $f_1$ (Figures \ref{basis_expansion_1_1} and \ref{basis_expansion_1_2}), which is especially pronounced for the lower signal-to-noise ratio. For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratio. The B-spline basis outperforms the Monomial basis in $f_2$, but comes second to the Fourier basis. While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ (Figures \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2}). With the low signal-to-noise ratio in the responses, the simulation chooses a smaller number of basis functions, which could be to prevent fitting this scalar noise using $\hat{\beta}(t)$.
	\vspace{-0.2cm}
